---
title: 'Class10: Scraping Multiple Webpages'
author: "Anna OConnell"
date: "2026-09-30"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives
- Enable you to scrape multiple web pages from same site, using a `for` loop type approach.
- Enable you to scrape multiple webpages from the same site, using the [purrr package](https://purrr.tidyverse.org/) which is a functional programming approach
*Note* We will make our own function

## Re-examining the bulletin example
Let su expand on last class to include the following 
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/),
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/),
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/), and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/).

*COMMENT* You can repeat your code few times without changing the url, this will work for a few links but would be quite tedious for large amounts of scraping. We will follow the **DRY Principle** which stands for *Dont Repeat Yourself**.


```{r Bulletin}
dept_abbrv  = c('acc', 'bus', 'isa', 'mkt')
courses_df = data.frame() # initializing the container to store stuff from loop
for (abbrv in dept_abbrv) 
  {
  cat(rep("-", 50, "\n"))
  print(abbrv)


bulletin_url = paste0(
  'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')

# we made this an r object instead of a str so we can reuse the rest of our code with only changing the url
webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs #Inspector to grab 


df = data.frame(title=titles, description=descs)
print(df$title[1:2])
courses_df = rbind(courses_df, df)
}

```


## `purrr` approach for the same problem

this is a funtional programming approach, and we will write our own function. In R we use the function called `function` to create a functiona s opposed to python, R functions return a single object

```{r purrr}
dept_abbrv  = c('acc', 'bus', 'isa', 'mkt')
# this fucntion takes an abbrv as an input and returns a data_frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0(
  'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/')

# we made this an r object instead of a str so we can reuse the rest of our code with only changing the url
webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs #Inspector to grab 


df = data.frame(title=titles, description=descs)
  return(df)
}

test = scrape_mu_bulletin(abbrv ='eco')

# Go get notes from this section from Fadel's doc or from Joe/Baiden
# .x is vector we will iterate over
# and the .f is the function we use
courses_df_from_purrr = purrr::map_df(.x = dept_abbrv, .f =scrape_mu_bulletin)

```

# Scrape data from website
The website we want to scrape is called www.planecrashinfo.com
```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, '.htm')
```










